Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2018-01-09 eurocg/paper.tex
kleinigkeit

%\renewcommand\windowpagestuff{%
%	\includegraphics{Reduction_visual}
%	\captionof{figure}{Example of three variable gadgets and\\ a satisfied clause gadget. Dotted parts do not belong\\ to the SPED.}
%	\label{fig:gadget_connection}
%}
%\opencutleft
\begin{proof}
%		\begin{cutout}{2}{0pt}{0.44\textwidth}{15}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$ that has a vertex for each variable $x_i$ and a vertex for each clause $c_j$.
	Each clause vertex is connected to the three variables appearing in the clause.
	In the drawing of $H_\phi$ all variable vertices are placed on a horizontal line and the clause vertices connect to the adjacent variable vertices either from above or from below the horizontal line.
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.
%		\end{cutout}

>>>>

%\renewcommand\windowpagestuff{%
%	\includegraphics{Reduction_visual}
%	\captionof{figure}{Example of three variable gadgets and\\ a satisfied clause gadget. Dotted parts do not belong\\ to the SPED.}
%	\label{fig:gadget_connection}
%}
%\opencutleft
\begin{proof}
%		\begin{cutout}{2}{0pt}{0.44\textwidth}{15}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$, which has a vertex for each variable $x_i$ and a vertex for each clause $c_j$.
	Each clause vertex is connected to the three variables appearing in the clause.
	In the drawing of $H_\phi$ all variable vertices are placed on a horizontal line and the clause vertices connect to the adjacent variable vertices either from above or from below the horizontal line.
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.
%		\end{cutout}
